BART: A Comparison with Non-bayesian Tree Methods

### 2024-12-02 paper/paper.tex
adding work on draft alone

\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{color}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{subcaption}
\usepackage{bookmark}
\usepackage[
    backend=biber,
    style=authoryear,
  ]{biblatex}

@@

Bagging uses a bootstrap sampling procedure to obtain different samples from the data, and then fits a tree for each of the bootstrapped samples. The single estimates for each sample are then averaged, as equation \ref{eq_bagging} shows. 
\begin{equation}
  \label{eq_bagging}
  \hat{f}_{\text{bag}}(x) = \frac{1}{B} \sum_{b=1}^{B} \hat{f}^{*b}(x).
\end{equation}
Where B is the number of samples of the bootstrapping procedure.

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{color}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{subcaption}
\usepackage{bookmark}
\usepackage[
    backend=biber,
    style=authoryear,
  ]{biblatex}

@@

Bagging uses a bootstrap sampling procedure to obtain different samples from the data, and then fits a tree for each of the bootstrapped samples. The single estimates for each sample are then averaged, as equation \ref{eq_bagging} shows. 
\begin{equation}
  \label{eq_bagging}
  \hat{f}_{\text{bag}}(x) = \frac{1}{B} \sum_{b=1}^{B} \hat{f}^{*b}(x).
\end{equation}
Where $B$ is the number of samples of the bootstrapping procedure.

@@

The number of sequential trees to fit, as chosen by the parameter $B$ in algorithm  \ref{alg_boosting}, if chosen too large, can cause overfitting. The learning rate $\lambda$ is another tunable parameter. Often small values are chosen ($\lambda=10^{-2}$ or even smaller).
